Download final data

### 2025-03-28 analysis/data-final.qmd
Launching site

- CSV file for any program
- `.rds` file for R <span class="small">(load with `df <- readRDS("weekly_panel.rds")`)</span>
- `.dta` file for Stata <span class="small">(load with `use "weekly_panel.dta"`)</span>

>>>>

- CSV file for any program
- `.rds` file for R <span class="small">(load with `df <- readRDS("data.rds")`)</span>
- `.dta` file for Stata <span class="small">(load with `use "data.dta"`)</span>
